module2_eco_pol_factors

### 2022-03-09 moduletwoanalysis.Rmd
fixed risk-benefit graphs in desceding order

@@

module2%>%
  filter(!row_number() %in% c(1,2)) %>% 
  select(starts_with("Ben"))%>%
  gather(Technology, Perceived_Benefit, Ben_Hydro:Ben_INDLPG, factor_key = TRUE)%>%
  separate(Technology, c("Ben", "Technology"), extra = "merge", fill = "left")%>%
  select(-Ben) %>%
  group_by(Technology, Perceived_Benefit) %>%
  summarise(n=n())%>%
ggplot(aes(fill= Perceived_Benefit, y=n, x=Technology)) + 
  geom_bar(position="fill", stat="identity")+
  coord_flip()

>>>>

likertstack <- module2%>%
  filter(!row_number() %in% c(1,2)) %>% 
  select(starts_with("RISKY"))%>%
  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
  select(-Risky) %>% 
  group_by(Technology, Perceived_Risk) %>%
  summarise(n=n()) %>%
  pivot_wider(names_from = "Perceived_Risk", values_from = "n")

likert(Measure ~ ., data=likertstack, ylab=NULL,
       ReferenceZero=3, as.percent=TRUE,
       positive.order=TRUE, 
       main = list("Pereived risk from energy technologies in India",x=unit(.55, "npc")), 
       sub= list("Perceived risk",x=unit(.57, "npc")), 
       xlim=c(-40,-20,0,20,40,60,80,100),
       strip=FALSE, 
       par.strip.text=list(cex=.7))
```

@@

colorsequence<- c("#8C4646","#D9695F","#F2A679","#F2D091","#5D8C7B","#808080")
df_barplotben <- module2%>%
  filter(!row_number() %in% c(1,2)) %>% 
  select(starts_with("Ben"))%>%
  gather(Technology, Perceived_Benefit, Ben_Hydro:Ben_INDLPG, factor_key = TRUE)%>%
  separate(Technology, c("Ben", "Technology"), extra = "merge", fill = "left")%>%
  select(-Ben) %>% 
  group_by(Technology, Perceived_Benefit) %>%
  summarise(n=n())

df_barplotben %>% ggplot(aes(fill= factor(Perceived_Benefit, levels=c("Extremely beneficial", "Very beneficial","Moderately beneficial","Slightly beneficial","Not at all beneficial","Rather not say/Don't know")), y=n , x=Technology)) + 
  geom_bar(position="fill",stat="identity")+
  scale_fill_manual("legend", values = c("Extremely beneficial" = "#5D8C7B", "Very beneficial" = "#F2D091", "Moderately beneficial" = "#F2A679", "Slightly beneficial" = "#D9695F","Not at all beneficial" = "#8C4646", "Rather not say/Don't know" = "#808080"))+
  coord_flip()+
  theme_classic()
